---
title: "Analisis of the datasets"
author: "A. Mora"
date: "24/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("~/Github/CooperativeFiltering")
options(digits=2)
```

```{r}
library(devtools)
devtools::load_all()
library(knitr)
library(arules)
library(fcaR)
library(Matrix)


library(tidyverse)
library(pmml)
library(sets)
library(magrittr)
# library("stringr")
# library(data.table)
# library(readxl)
# #library(readr)

library(foreach)
library(doParallel)
library(doSNOW)

 
library(dplyr)
library(readr)
library(tidyr)
 options(digits = 2)  
 op = function(x, d=2) sprintf(paste0("%1.",d,"f"), x) 
```


# Analysis of results

## Celeb dataset


First, we prepare the summary with the results of the experiment:

```{r}


setwd("~/Github/CooperativeFiltering")
celeb <- read_csv("datasets/list_attr_celeba.csv")
 indicex <- celeb==-1
celeb[indicex] <- 0

rows_celeb <- dim(celeb)[1]
 

celeb_sparsity <- sum(celeb == 0)/(dim(celeb)[1]*dim(celeb)[2])
cat('Sparsity of the dataset:',celeb_sparsity)

celeb_sizes <- read.csv("Ejemplos-pruebas/celeb_sizes_1000executions_attriubutes.csv")


summary_by_iteration_celeb_sizes <- celeb_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
    n = n(),
    max_objects = max(objects, na.rm = TRUE),
  )  %>%
  mutate(prunning_objects = 100-(max_objects/rows_celeb)*100)

summary_by_iteration_celeb_sizes








```




## DSK dataset

First, we prepare the summary with the results of the experiment:




```{r}


setwd("~/Github/CooperativeFiltering")
DSK <- read.csv("datasets/all_pivoted.csv")
DSK_sparsity <- sum(DSK == 0)/(dim(DSK)[1]*dim(DSK)[2])
cat('Sparsity of the dataset:',DSK_sparsity)

rows_DSK <- dim(DSK)[1]

DSK_sizes <- read.csv("Ejemplos-pruebas/diseases_sizes_1000_attributes.csv")

 

summary_by_iteration_DSK_sizes <- DSK_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
    n = n(),
    max_objects = max(objects, na.rm = TRUE),
  )  %>%
  mutate(prunning_objects = 100-(max_objects/rows_DSK)*100)

summary_by_iteration_DSK_sizes

```



## HPO dataset

First, we prepare the summary with the results of the experiment:

```{r}

setwd("~/Github/CooperativeFiltering")

HPO <- read.csv("datasets/TB_1_2.csv", sep=";")
HPO_sparsity <- sum(HPO == 0)/(dim(HPO)[1]*dim(HPO)[2])
cat('Sparsity of the dataset:',HPO_sparsity)

rows_HPO <- dim(HPO)[1]

HPO_sizes <- read.csv("Ejemplos-pruebas/tbl1_sizes_1000_attributes.csv")

 

summary_by_iteration_HPO_sizes <- HPO_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
    n = n(),
    max_objects = max(objects, na.rm = TRUE),
  )  %>%
  mutate(prunning_objects = 100-(max_objects/rows_HPO)*100)

summary_by_iteration_HPO_sizes

```



## Length of the dialogue with users

```{r, fig.width=15,fig.align="center"}
# Source 
# https://www.datanovia.com/en/blog/ggplot-multiple-plots-made-ridiculuous-simple-using-patchwork-r-package/

library(ggplot2)
library(patchwork)
library(gridExtra)
# 0. Define custom color palette and prepare the data
my3cols <- c("#E7B800", "#2E9FDF", "#FC4E07")

p_celeb <- ggplot(summary_by_iteration_celeb_sizes, aes(x=step, y = n))

lp_celeb <- ggplot(summary_by_iteration_celeb_sizes, aes(x = step, y = n)) + 
  geom_line(color = "#E46726") +
  geom_label(aes(label = n), data = summary_by_iteration_celeb_sizes, nudge_y = 3, alpha = 0.5)+
    labs(title = " Celebface dataset", x= " Number of steps", y="Number of simulations")

p_DSK <- ggplot(summary_by_iteration_DSK_sizes, aes(x=step, y = n))

 

lp_DSK <- ggplot(summary_by_iteration_DSK_sizes, aes(x = step, y = n)) + 
  geom_line(color = "#FC4E07")+
  geom_label(aes(label = n), data = summary_by_iteration_DSK_sizes, nudge_y = 3, alpha = 0.5)+
    labs(title = "DSK dataset", x= " Number of steps", y="Number of simulations") 


p_HPO <- ggplot(summary_by_iteration_HPO_sizes, aes(x=step, y = n))

 

lp_HPO <- ggplot(summary_by_iteration_HPO_sizes, aes(x = step, y = n)) + 
  geom_line(color = "#FC4E07")+
  geom_label(aes(label = n), data = summary_by_iteration_HPO_sizes, nudge_y = 3, alpha = 0.5)+
    labs(title = "HPO dataset", x= " Number of steps", y="Number of simulations") 

lp_together <- lp_celeb + lp_DSK  + lp_HPO
lp_together
 
ggsave("experiment_len_dialogue.pdf",plot = lp_together)

```


## HPO comparison

Comparing our results with Cooperative Filtering recommender with [Benito 2018].

```{r}
summary_by_iteration_HPO_sizes
cat('Experiments finishing in  2 steps',(1000-456)/1000*100,"%")
cat('Experiments finishing in 3 steps',(1000-(19))/1000*100,"%")
cat('Experiments finishing in  4 steps',0,"%")


```



## Velocity of the recommendation

The greater the amount of objects recommended in each step, the greater the velocity of the recommender. 

```{r,fig.width=5, fig.height=10}


summary_objects1 <- celeb_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
    n = n(),
    mean_objects_celeb = mean(objects, na.rm = TRUE),
  )   

summary_objects1

summary_objects2 <- DSK_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
    n = n(),
    mean_objectsDSK = mean(objects, na.rm = TRUE)
  )  

summary_objects2



summary_objects3 <- HPO_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
    n = n(),
    mean_objectsHPO = mean(objects, na.rm = TRUE)
  )  

summary_objects2


summary_objects <- summary_objects1 %>%
  left_join(summary_objects2, by = "step")
summary_objects
 
  
summary_objects <- summary_objects %>%
  left_join(summary_objects3, by = "step") 


summary_objects$mean_objects_celeb   %>% replace_na(0)
  
summary_objects$mean_objectsDSK   %>% replace_na(0)

summary_objects$mean_objectsHPO   %>% replace_na(0)


summary_objects


 

lp_objects <- ggplot(summary_objects, aes(x = step, y =mean_objects_celeb )) + 
  geom_line(color = "#FC4E07")+
    labs(title = "celebA dataset", x= " Number of steps of the dialogue", y="Number of objects recommended") 
  

lp_objects2 <- ggplot(summary_objects, aes(x = step, y =mean_objectsDSK )) + 
  geom_line(color = "#FC4E07")+
    labs(title = "DSK dataset", x= " Number of steps of the dialogue", y="Number of objects recommended") 
  
lp_objects3 <- ggplot(summary_objects, aes(x = step, y =mean_objectsHPO )) + 
  geom_line(color = "#FC4E07")+
    labs(title = "HPO dataset", x= " Number of steps of the dialogue", y="Number of objects recommended") 
  
library(gridExtra)
library(grid)

table_summary_objects  <- summary_objects %>%
  select(c(step,starts_with("mean")))%>% 
  rename("celeb"=mean_objects_celeb)%>% 
  rename("DSK"=mean_objectsDSK)%>% 
  rename("HPO"=mean_objectsHPO)
 
table_summary_objects <- table_summary_objects %>% replace(., is.na(.), 0)

table_summary_objects <- formatC(as.matrix(table_summary_objects),digits = 0,format = "f")

 

lp_objects_together <- lp_objects / lp_objects2    / lp_objects3 /  tableGrob(table_summary_objects, rows=NULL, cols = NULL)

#lp_objects_together <- (lp_objects | lp_objects2   ) / (lp_objects3 |  tableGrob(table_summary_objects, rows=NULL, cols = NULL))

lp_objects_together
 
ggsave("experiment_objects.pdf",plot = lp_objects_together)
 
 
  
 
```


## Attributes suggested to the user

Finally we study the number of attributtes suggested to the user in each step of the dialogue.

```{r,fig.width=5, fig.height=10}

summary_attr1 <- celeb_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
     mean_attr_celeb = mean(attributes, na.rm = TRUE),
  )   

summary_attr2 <- DSK_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
     mean_attrDSK = mean(attributes, na.rm = TRUE),
  )   
summary_attr3 <- HPO_sizes %>%
  rename(step =iteration) %>%
  group_by(step) %>%
  summarise(
     mean_attrHPO = mean(attributes, na.rm = TRUE),
  )   


summary_attributes <- summary_attr1 %>%
  left_join(summary_attr2, by = "step")
summary_attributes
 
  
summary_attributes <- summary_attributes %>%
  left_join(summary_attr3, by = "step") 


table_summary_attributes <- summary_attributes %>% replace(., is.na(.), 0) 

 
 
lp_attr1 <- ggplot(table_summary_attributes, aes(x = step, y =mean_attr_celeb )) + 
  geom_line(color = "#FC4E07")+
    labs(title = "celebA dataset", x= " Number of steps of the dialogue", y="Number of attributes suggested ") 
  

lp_attr2 <- ggplot(table_summary_attributes, aes(x = step, y =mean_attrDSK )) + 
  geom_line(color = "#FC4E07")+
    labs(title = "DSK dataset", x= " Number of steps of the dialogue", y="Number of attributes suggested") 
  
lp_attr3 <- ggplot(table_summary_attributes, aes(x = step, y =mean_attrHPO )) + 
  geom_line(color = "#FC4E07")+
    labs(title = "HPO dataset", x= " Number of steps of the dialogue", y="Number of attributes suggested") 
  
table_summary_attributes  <- table_summary_attributes %>%
  select(c(step,starts_with("mean")))%>% 
  rename("celeb"=mean_attr_celeb)%>% 
  rename("DSK"=mean_attrDSK)%>% 
  rename("HPO"=mean_attrHPO)

table_summary_attributes <- formatC(as.matrix(table_summary_attributes),digits = 0,format = "f")

#lp_attr_together <- (lp_attr1 | lp_attr2  | lp_attr3) / tableGrob(table_summary_attributes, rows=NULL, cols = NULL)

lp_attr_together <- lp_attr1 / lp_attr2  / lp_attr3 / tableGrob(table_summary_attributes, rows=NULL, cols = NULL)

lp_attr_together

 
ggsave("experiment_attr.pdf",plot = lp_attr_together)

```


## General information of dataset



We extract the rules:
```{r}

FC <- read_csv("/Volumes/GoogleDrive/Mi unidad/CooperativeFiltering/datasets/list_attr_celeba.csv")
indicex <- FC==-1
FC[indicex] <- 0

colnames(FC)
filas <- rownames(FC)
FC1 <-as.data.frame(sapply(FC[,2:41], function(x) as.logical(x)))

my_support <- 0.001
rule_param = list(
  supp = my_support,
  conf = 1,
  maxlen = 15
) 
celeb_rules <- apriori(FC1,parameter = rule_param)
celeb_rules1 <- celeb_rules[!is.redundant(celeb_rules)]

 
fc <- FormalContext$new(FC1)
fc$implications$add(celeb_rules1)

celeb_fc_left <- lhs.minimals(fc$implications)
celeb_attributes_left <- celeb_fc_left@Dim[1]
celeb_attributes_left     
 


FC <- read.csv("/Volumes/GoogleDrive/Mi unidad/CooperativeFiltering/datasets/TB_1_2.csv", sep=";")

colnames(FC)
filas <- rownames(FC)
rownames(FC) <- FC$DISEASE_ID
FC$DISEASE_ID <- NULL

FC1 <-as.data.frame(sapply(FC, function(x) as.logical(x)))
#View(head(FC1))



my_support <- 0.0095
rule_param = list(
  supp = my_support,
  conf = 1,
  maxlen = 25
)

HBO_rules <- apriori(FC1,parameter = rule_param)
HBO_rules1 <- HBO_rules[!is.redundant(HBO_rules)]

fc1 <- FormalContext$new(FC1)
fc1$implications$add(HBO_rules1)

HBO_f1_left <- lhs.minimals(fc1$implications)
HBO_attributes_left <- HBO_f1_left@Dim[1]
HBO_attributes_left   


FC <- read.csv("/Volumes/GoogleDrive/Mi\ unidad/CooperativeFiltering/datasets/sytora-master/data/all-files-for-ml/all_pivoted.csv")



head(FC[,1:24])

rownames(FC) <- FC$Disease
filas <- rownames(FC)

FC$Disease <- NULL
 
FC1 <-as.data.frame(sapply(FC, function(x) as.logical(x)))
#View(head(FC1))

my_support <- 0.005
rule_param = list(
  supp = my_support,
  conf = 1,
  maxlen = 30
)

DSK_rules <- apriori(FC1,parameter = rule_param)
DSK_rules1 <- DSK_rules[!is.redundant(DSK_rules)]

fc1 <- FormalContext$new(FC1)
fc1$implications$add(DSK_rules1)

DSK_f1_left <- lhs.minimals(fc1$implications)
DSK_attributes_left <- DSK_f1_left@Dim[1]
DSK_attributes_left   
```
 

```{r}

datasets3 <- data.frame(celebA=c(dim(celeb)[2]),
                        DSK=c(dim(DSK)[2]),
                        HPO=c(dim(HPO)[2]))

datasets3b <- data.frame(celebA=c(dim(celeb)[1]),
                        DSK=c(dim(DSK)[1]),
                        HPO=c(dim(HPO)[1]))

datasets3c <- data.frame(celebA=c(format(celeb_sparsity,digits = 2)),
                        DSK=c(format(DSK_sparsity,digits = 2)),
                        HPO=c(format(HPO_sparsity,digits = 2)))


datasets3d <- data.frame(celebA=c(length(celeb_rules1)),
                        DSK=c(length(DSK_rules1)),
                        HPO=c(length(HBO_rules1)))

datasets3e <- data.frame(celebA=c(celeb_attributes_left),
                        DSK=c(DSK_attributes_left),
                        HPO=c(HBO_attributes_left))


datasets3 <- rbind(datasets3,datasets3b)
datasets3 <- rbind(datasets3,datasets3c)
datasets3 <- rbind(datasets3,datasets3d)
datasets3 <- rbind(datasets3,datasets3e)

rownames(datasets3) <- c("Columns","Rows","Sparsity","Implications","Attr.Left")
 



lp_summary <-  tableGrob(datasets3)



ggsave("experiment_lp_summary.pdf",plot = lp_summary)

                        
```


## Figure 7

Comparison with [Benito 2018]:
```{r}
df_comparison <- data.frame("1 Step"=c(0,0),
                        "2 Steps"=c(68,54.4),
                        "3 Steps"=c(26,43.7),
                        "4 Steps"=c(5,0),
                        "5 Steps"=c(1,0)
                        )

colnames(df_comparison) <- c("1 Step","2 Steps","3 Steps","4 Steps","5 Steps")
rownames(df_comparison) <- c("Benito2018","Cooper.Filt.")

rownames(df_comparison)
lp_comparison <-   tableGrob(df_comparison)

  

 

ggsave("experiment_lp_comparison.pdf",plot = lp_comparison)


```

